Congestion-Aware Join Optimization in Key-Value Stores

### 2014-08-07 paper/paper.tex
Additional future work paragraph

>>>>

While our results are promising, we would like to take a more principled approach to determine the theoretical gains possible for applying this technique in order to clearly identify potential bottlenecks.
We are also interested in performing a more thorough evaluation on a larger scale with more realistic conditions.
We feel that there is potential to significantly improve the performance of our current approach.
For example, we currently buffer all results at each server before sending a reply.
Streaming results back to the client as they are received may result in higher link utilization and increased efficiency.
